Flagging gravitational wave sources from radio jet morphology

### 2015-04-03 Paper/paper.tex
Add latest plots

>>>>

\begin{figure*}
\begin{center}
  \begin{tabular}{cc}
    \includegraphics*[width=\columnwidth]{{jet_i40_beta0.90_mdot1.0_full}.pdf} &
    \includegraphics*[width=\columnwidth]{{jet_i40_beta0.90_mdot1.0_zoom1}.pdf} 
  \end{tabular}
\end{center}
\caption{$a^4/M^3=1$}
\label{fig:jet_mdot1.0}
\end{figure*}

\begin{figure*}
\begin{center}
  \begin{tabular}{cc}
    \includegraphics*[width=\columnwidth]{{jet_i40_beta0.90_mdot10.00_full}.pdf} &
    \includegraphics*[width=\columnwidth]{{jet_i40_beta0.90_mdot10.00_zoom1}.pdf} 
  \end{tabular}
\end{center}
\caption{$a^4/M^3=10$}
\label{fig:jet_10.0}
\end{figure*}

\begin{figure*}
\begin{center}
  \begin{tabular}{cc}
    \includegraphics*[width=\columnwidth]{{jet_i40_beta0.90_mdot0.10_full}.pdf} &
    \includegraphics*[width=\columnwidth]{{jet_i40_beta0.90_mdot0.10_zoom1}.pdf} 
  \end{tabular}
\end{center}
\caption{$a^4/M^3=0.1$}
\label{fig:jet_mdot0.1}
\end{figure*}
